### 2010-12-12 docs/tex/review.tex
`complex adaptive system' more or less complete

\subsection{Complex Adaptive System}
The following definition of Complex Adaptive System is the most comprehensive.

@@

\subsection{Echo}
Echo is simulation of a Complex Adaptive System. It is more of a gedanken experiment rather than a precise simulation.

>>>>

\subsection{Complex Adaptive System}
\label{subsec:complex-adaptive-system}
Complex adaptive systems (CAS) are special cases of complex systems. They are complex as they are diverse and made up of multiple interconnected elements and adaptive as they have the capacity to change and learn from experience. Examples of complex adaptive systems include the stock market, social insect and ant colonies, the biosphere and the ecosystem, the brain and the immune system, the cell and the developing embryo, manufacturing businesses and any human social group-based endeavor in a cultural and social system such as political parties or communities. This includes some large-scale online systems, such as collaborative tagging or social bookmarking systems.

The following definition of Complex Adaptive System is comprehensive.

@@

Holland also provides some common kernel of similarities and dissimilarities between different complex adaptive systems in \textsl{Adaptation in Natural and Artificial Systems} \cite{holland1975}:

\begin{enumerate}
	\item \textsl{``All complex adaptive system involves large number of parts undergoing a kaleidoscopic array of simultaneous non linear interactions."}
	\item \textsl{``The impact of these systems in human affairs centers on the aggregate behavior, the behavior of the whole."}
	\item \textsl{``The interactions evolve over time, as the parts adapt in an attempt to survive in the environment provided by the other parts."}
	\item \textsl{``Complex adaptive systems anticipate."}
\end{enumerate}

\subsection{Echo}
Echo is a class of simulation model of a complex adaptive system, designed primarily for gedanken experiments rather than a precise simulation. Echo provides, for the study of populations of evolving, reproducing agents distributed over a geography, with different inputs of renewable resources at various sites. Each agent has simple capabilities - offense, defense, trading and mate selection - defined by a set of chromosomes. Even though these capabilities are simple and defined simply, they provide a rich set of variations illustrating the four kernel properties of complex adaptive systems described in section \ref{subsec:complex-adaptive-system}.
